Illusion Sensitivity and Phenomenological Control

### 2025-05-20 analysis/1_cleaning.qmd
simplify: remove SD per dim

---
title: "Illusion Game & PCS"
subtitle: "Preprocessing"
date: "`r Sys.Date()`"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

```{r}
SD_per_dim <- function(x, dims="") {
  m <- matrix(nrow=nrow(x), ncol=0)
  for(s in dims) {
    m <- cbind(m, sapply(as.data.frame(t(x[grepl(s, names(x))])), sd))
  }
  m
}
```

@@

data_ppt$IPIP6_Extraversion <- rowMeans(ipip6[grepl("ext", names(ipip6))])
data_ppt$IPIP6_Conscientiousness <- rowMeans(ipip6[grepl("cons", names(ipip6))])
data_ppt$IPIP6_Neuroticism <- rowMeans(ipip6[grepl("neuro", names(ipip6))])
data_ppt$IPIP6_Openness <- rowMeans(ipip6[grepl("open", names(ipip6))])
data_ppt$IPIP6_HonestyHumility <- rowMeans(ipip6[grepl("honhum", names(ipip6))])
data_ppt$IPIP6_Agreeableness <- rowMeans(ipip6[grepl("agr", names(ipip6))])
data_ppt$IPIP6_SD <- rowMeans(SD_per_dim(ipip6, c("Extraversion", "Conscientiousness", "Neuroticism", "Openness", "HonestyHumility", "Agreeableness")))

# data_ppt$IPIP6_Extraversion <- rowMeans(ipip6[grepl("Ext", names(ipip6))])
# data_ppt$IPIP6_Conscientiousness <- rowMeans(ipip6[grepl("Cons", names(ipip6))])
# data_ppt$IPIP6_Neuroticism <- rowMeans(ipip6[grepl("Neuro", names(ipip6))])
# data_ppt$IPIP6_Openness <- rowMeans(ipip6[grepl("Ppen", names(ipip6))])
# data_ppt$IPIP6_HonestyHumility <- rowMeans(ipip6[grepl("HonHum", names(ipip6))])
# data_ppt$IPIP6_Agreeableness <- rowMeans(ipip6[grepl("Agr", names(ipip6))])
# data_ppt$IPIP6_SD <- rowMeans(SD_per_dim(ipip6, c("Extraversion", "Conscientiousness", "Neuroticism", "Openness", "HonestyHumility", "Agreeableness")))
```

@@

data_ppt$PID5_Disinhibition <- rowMeans(pid5[grepl("Dis", names(pid5))])
data_ppt$PID5_Detachment <- rowMeans(pid5[grepl("Det", names(pid5))])
data_ppt$PID5_NegativeAffect <- rowMeans(pid5[grepl("NegAff", names(pid5))])
data_ppt$PID5_Antagonism <- rowMeans(pid5[grepl("Ant", names(pid5))])
data_ppt$PID5_Psychoticism <- rowMeans(pid5[grepl("Psy", names(pid5))])
data_ppt$PID5_SD <- rowMeans(SD_per_dim(pid5, c("Disinhibition", "Detachment", "NegativeAffect",
                                             "Antagonism", "Psychoticism")))
```

>>>>

---
title: "Illusion Sensitivity and Phenomenological Control"
subtitle: "Preprocessing"
date: "`r Sys.Date()`"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

@@

data_ppt$IPIP6_Extraversion <- rowMeans(ipip6[grepl("ext", names(ipip6))])
data_ppt$IPIP6_Conscientiousness <- rowMeans(ipip6[grepl("cons", names(ipip6))])
data_ppt$IPIP6_Neuroticism <- rowMeans(ipip6[grepl("neuro", names(ipip6))])
data_ppt$IPIP6_Openness <- rowMeans(ipip6[grepl("open", names(ipip6))])
data_ppt$IPIP6_HonestyHumility <- rowMeans(ipip6[grepl("honhum", names(ipip6))])
data_ppt$IPIP6_Agreeableness <- rowMeans(ipip6[grepl("agr", names(ipip6))])
```

@@

data_ppt$PID5_Disinhibition <- rowMeans(pid5[grepl("Dis", names(pid5))])
data_ppt$PID5_Detachment <- rowMeans(pid5[grepl("Det", names(pid5))])
data_ppt$PID5_NegativeAffect <- rowMeans(pid5[grepl("NegAff", names(pid5))])
data_ppt$PID5_Antagonism <- rowMeans(pid5[grepl("Ant", names(pid5))])
data_ppt$PID5_Psychoticism <- rowMeans(pid5[grepl("Psy", names(pid5))])
```

### 2025-05-20 analysis/2_analysis.qmd
simplify: remove SD per dim

---
title: "Illusion Game & PCS"
subtitle: "Analysis"
date: "`r Sys.Date()`"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    warning: false 
    message: false 
execute: 
  cache: true
---

>>>>

---
title: "Illusion Sensitivity and Phenomenological Control"
subtitle: "Analysis"
date: "`r Sys.Date()`"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
    warning: false 
    message: false 
execute: 
  cache: true
---
